Correlation tests

### 2025-03-19 analysis/cor_tables.qmd
Try again

---
title: "Correlation tests"
format: 
    gfm:
      echo: true
      message: false
      warning: false
      code-fold: true
---

@@

```{r}

cor_articles <- create_correlation_table(my_df_ind, vars = c("hoad_articles", "scp_first_author_articles", "wos_first_author_articles", 
            "scp_corresponding_author_articles", "wos_corresponding_author_articles"), "Article volume")
create_gt_upper_triangle(cor_articles)
```

>>>>

---
title: "Correlation tests"
format: 
    gfm:
      echo: true
      message: false
      warning: false
      code-fold: true
prefer-html: true
---

@@

```{r}
cor_articles <- create_correlation_table(my_df_ind, vars = c("hoad_articles", "scp_first_author_articles", "wos_first_author_articles", 
            "scp_corresponding_author_articles", "wos_corresponding_author_articles"), "Article volume")
create_gt_upper_triangle(cor_articles)
```
